Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
modified overview

\subsection{Overview}
Our method attempts to match CAD models to 2D images, determining the best
model within a class, its pose and scale, and the focal length of the camera
used to produce the image. These parameters are first coarsely estimated using
a discrete bank of detectors trained offline, before they are refined using
MCMC by generating new detectors on the fly.

The basic detection method underlying our approach is HOG template matching.
However, we propose a new HOG variant called Non-Zero Whitened Histograms of
Orientations (NZ-WHO), where the HOG templates are whitened using statistics
found from a random collection of natural images, producing a more
discriminative template.

In addition to the library of CAD models that will be matched to the query
images, our method requires a collection of random natural images. Offline, we
compute HOG features of these images and record their mean and spatial
autocovariance. The images are not used during testing, only the statistics
generated from them.

@@

Optionally, our algorithm can be initialized using proposal bounding boxes from
state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
executing the two steps above. In this scenario, our approach provides a means
to augment standard bounding box detectors with more interesting 3D
information.

@@

@@

Hariharan \etal. interpreted the
whitening as Linear Discriminant Analysis (LDA) where all classes have different
means but have the same covariance. The whitening and LDA have the same
formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
where $\mu_+$ is the features from a class (LDA) or a signal to whiten
(whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
(whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
the correlation within signal (whitening).

@@

\subsubsection{Generating $\Sigma$ and $\mu$}
\scream{this section seems important to understand the following section but it's also just a re-writing of the Hariharan method}
In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
generated from natural images. That is, they assume the mean of a HOG cell is
independent of its place in the image, and the autocovariance of cells depends
only on their relative location.

@@

>>>>

\subsection{Overview}
Our method attempts to match CAD models to 2D images, determining the best
model within a class, its pose and scale, and the focal length of the camera
used to produce the image. These parameters are first coarsely estimated using
an ensemble of templates generated offline, before they are refined using
MCMC by generating new detectors on the fly.

% The basic detection method underlying our approach is WHO template matching.
% However, we propose a new WHO variant called Non-Zero Whitened Histograms of
% Orientations (NZ-WHO), where the variant of WHO templates are made from 
% synthetic rendering to with

Our method In addition to the library of CAD models that will be matched to the query
images, our method requires a feature statistics which can be collected once and for all.

% images, our method requires a collection of random natural images. Offline, we
% compute HOG features of these images and record their mean and spatial
% autocovariance. The images are not used during testing, only the statistics
% generated from them.

@@

Our ensemble of NZ-WHO templates can work as a detector but our algorithm 
can be initialized using proposal bounding boxes from
state-of-the-art object detectors \cite{Felzenszwalb10,Girshick14} before
executing the two steps above. In this scenario, our approach provides a means
to augment standard bounding box detectors with more interesting 3D
information.

@@

We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
continuously.

@@

Hariharan \etal. explained the
whitening as Linear Discriminant Analysis (LDA) where all classes have different
means but have the same covariance.

% The whitening and LDA have the same
% formulation when we make a decision boundary $w = \Sigma^{-1}(\mu_+ - \mu_0)$
% where $\mu_+$ is the features from a class (LDA) or a signal to whiten
% (whitening), $\mu_0$ is the negative class center (LDA) or the signal mean
% (whitening) and $\Sigma$ is the covariance matrix of classes (LDA) or
% the correlation within signal (whitening).

@@

\subsubsection{Non-Zero Covariance}
In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
generated from natural images. That is, they assume the mean of a HOG cell is
independent of its place in the image, and the autocovariance of cells depends
only on their relative location.

@@

Our method requires generating a covariance matrix of non-zero cells
